Variation in distance between consecutive animal locations

### 2021-03-31 distributions_paper/rudolph_distributions.Rmd
moved around. Intro draft ready. Methods first paragraph

@@

We focused our study of individual variation on the many-banded araçari (*Pterglossus pluricinctus*), a small toucan in Yasuní National Park, Ecuador. We used previously collected data from studies using radiotelemetry to estimate home ranges and evaluate the potential seed dispersal distances for the *Virola flexuosa* tree [@holbrook2011home, holbrook2007usin]. Over a period of four years, from 2001 to 2005, *P. pluricinctus* individuals were captured and radio-transmitters were attached at the base of the central tail feathers [@holbrook2011home]. Toucan locations were estimated by triangulation using receivers and hand-held antennas, with tracking periods lasting between 4-5 hours per day, locating individual birds every 15 minutes. Further details on field methods can be found in Holbrook [-@holbrook_home_2011]. It is important to note that these methods did not tack all birds simultaneously, and that although individual toucan locations were attempted every 15 minutes, this was not always possible, thus some successive locations have time categories associated to multiples of 15. For our analyses, we focused on toucans with a minimum of **20?** recorded locations, and we calculated turning angles (in radians), and the associated Euclidean step lengths in meters for each successive set of locations and turning directions. We worked under a velocity-based framework, and thus divided step lengths by the time interval during which they were recorded. This gave us a total of **600ish?** data points for turning angles and velocities.

>>>>

We focused our study of individual variation on the many-banded araçari (*Pterglossus pluricinctus*), a small toucan in Yasuní National Park, Ecuador. We used previously collected data from studies using radiotelemetry to estimate home ranges and evaluate the potential seed dispersal distances for the *Virola flexuosa* tree [@holbrook2011home, holbrook2007usin]. Over a period of four years, from 2001 to 2005, *P. pluricinctus* individuals were captured and radio-transmitters were attached at the base of the central tail feathers [@holbrook2011home]. Toucan locations were estimated by triangulation using receivers and hand-held antennas, with tracking periods lasting between 4-5 hours per day, locating individual birds every 15 minutes. Further details on field methods can be found in Holbrook [-@holbrook2011home]. It is important to note that these methods did not tack all birds simultaneously, and that although individual toucan locations were attempted every 15 minutes, this was not always possible, thus some successive locations have time categories associated to multiples of 15. <span style="color:red">For our analyses, we focused on toucans with a minimum of **20?** recorded locations, and we calculated turning angles (in radians), and the associated Euclidean step lengths in meters for each successive set of locations and turning directions. We worked under a velocity-based framework, and thus divided step lengths by the time interval during which they were recorded. This gave us a total of **600ish?** data points for turning angles and velocities.red</span>

@@
